### 2021-06-08 sections/strategy_Htautau.tex
Implemented referee comments
update
first draft version

%-------------------------------------------------------------------------------
\section{Strategy for the $\Htautau$ search}
\label{sec:strategy_Htautau}
%-------------------------------------------------------------------------------

The analysis strategy adopted in the $\Htautau$ search closely follows that developed in Ref.~\cite{Chen:2015nta} and is summarised in this section.

@@

In the $\Htautau$ search, the $\ttbar \to WbHq$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson and at least four jets, only one of which originates from a $b$-quark.
%In the $\Htautau$ search, the final state signature of interest is characterised by the presence of two $\tau$-leptons from the
%decay of the Higgs boson as well as a light-quark jet, the latter two originating from the decay of one of the top quarks. 
If one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
%The other top quark decays into a $W$ boson and a $b$-quark, with the $W$ boson in turn decaying hadronically, resulting in 
%three additional jets. Therefore, at least four jets are typically expected in signal events.
However, in a significant fraction of the events the lowest-$\pt$ jet from the $W$ boson decay fails the minimum $\pt$ requirement of $30~\gev$,
resulting in signal events with only three jets reconstructed.
In order to optimise the sensitivity of the search, the selected events are categorised into four SRs depending 
on the number of $\taulep$ and $\had$ candidates, and on the number of jets:
($\lephad$, 3j), ($\lephad$, $\geq$4j), ($\hadhad$, 3j), and ($\hadhad$, $\geq$4j).

This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
is missing or not (events with exactly three jets or at least four jets).
%This analysis adopts the event reconstruction strategy developed in Ref.~\cite{Chen:2015nta}, which is briefly summarised in the following. 
%The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
The event reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}.

Events with exactly three jets that are compatible with having a fully reconstructed hadronically decaying 
top quark ($t \to Wb \to qqb$) are rejected, as the $t \to Hq$ decay cannot be reconstructed due to the missing light-quark jet.
This compatibility is assessed via a likelihood function that depends on the reconstructed mass of the three-jet 
system and the two non-$b$-tagged jets.
For the remaining events, the selected jets are assigned to the different top-quark decay products via a criterion based on 
minimising a sum of angular distances between objects. Finally, the four-momenta of the invisible decay products for each $\tau$-lepton decay 
are estimated by minimising a $\chi^2$ function based on the probability density functions for the angular distance of the visible and invisible
products of the $\tau$-lepton decay, and including Gaussian constraints on the $\tau$-lepton mass, the Higgs boson mass and the
measured $\met$. After the $\chi^2$ minimisation, the Higgs boson four-momentum, and hence its invariant mass, as well as the 
four-momentum of the parent top quark, are determined with better resolution. Following the event kinematic reconstruction, several kinematic variables
that discriminate between signal and background are defined. These variables are used in the multivariate analysis discussed in the next section.

%To comply with the signal topology, in each event, exactly one jet should be tagged as a $b$-jet. If all jets from the top hadronic decay and the jet from $t\to Hq$, denoted as the FCNC jet, pass the jet selection, there should be at least four jets. However, some jets have a $\pt$ less than 30 GeV and may fail to pass the jet selection. The most likely missing jet is the subleading jet from the $W$ decay. These 3-jet events are still kept if the FCNC jet can be found and matched with the Higgs to reconstruct the top. It is done as follows. In the 3-jet events, if the three jets, denoted by $j_1$, $j_2$, $b$, satisfy
%\begin{equation}
%\chi_{Wb}^2 \equiv \left(\frac{m_{j_1 j_2}-80.4}{20}\right)^2 + \left(\frac{m_{j_1 j_2 b}-172.5}{25}\right)^2 <5,
%\label{eq:chi2-3jet}
%\end{equation}
%where the mass is in GeV, the event is discarded. In these events, a good hadronic top is reconstructed, but the FCNC jet from the other top is missing.
%
%If Eq.~(\ref{eq:chi2-3jet}) is not satisfied, the FCNC jet is identified by the least sum of angular distances, $\Delta R_{3j}$, expressed as 
%\begin{equation}
%\Delta R_{3j} \equiv \Delta R(j_c ,H) + \Delta R(j_W ,b) \: ,
%\label{eq:deltaR-3jet}
%\end{equation}
%where the $j_W$ denotes the jet from the $W$ decay, and the event is kept.
%
%For the events with at least four jets (denoted as 4-jet events), the three leading ones other than the $b$-jet are considered. Out of the three possible combinations that form the two sets of top decay products, the one with the least sum of angular distances, $\Delta R_{4j}$, is chosen, which is defined as
%\begin{equation}
%\Delta R_{4j} \equiv \Delta R(j_c ,H) + \Delta R(j_{1} ,b) + \Delta R(j_{2} ,b) + \Delta R(j_{1} ,j_{2}),
%\label{eq:deltaR-4jet}
%\end{equation}
%where $j_{1,2}$ are the jets from the $W$ decay. No explicit $c$-tagging is used, and as can be seen above, the FCNC jet is found through pure kinematic criteria such as $\Delta R$.
%
%The method introduced in \cite{Chen:2015nta} is used to recontruct the ditau mass and momentum by taking the tau decay kinematics into account. To determine the 4-momenta of the invisible decay products of the tau decays, the following $\chi^2$ in Eq.~\ref{eq:tautau-chi2}, based on the probability functions above and the constraints from the tau mass, the Higgs mass and the measured $\met$, is defined,
%\begin{eqnarray}
%\begin{array}{ll}
%\chi^2 = & -2\ln \mathcal{P}_1 -2\ln \mathcal{P}_2 + \left( \frac{m_{\tau_1}^{\text{fit}} - 1.78}{\sigma_{\tau}} \right)^2 +  \left( \frac{m_{\tau_2}^{\text{fit}} - 1.78}{\sigma_{\tau}} \right)^2 +  \left( \frac{m_{H}^{\text{fit}} - 125}{\sigma_{\text{Higgs}}} \right)^2 + \\
% & \left( \frac{E_{x,\text{miss}}^{\text{fit}} - E_{x,\text{miss}}}{\sigma_{\text{miss}}} \right)^2 + \left( \frac{E_{y,\text{miss}}^{\text{fit}} - E_{y,\text{miss}}}{\sigma_{\text{miss}}} \right)^2 ,
%\end{array}
%\label{eq:tautau-chi2}
%\end{eqnarray}
%where $\mathcal{P}_i(\Delta R)$ are the probability distributions of the angular distance of the visible and invisible decay products in the tau decay, parametrized as a function of the momentum of the tau lepton. In the $\taulep$ mode where two neutrinos are present, it is extended to be the joint probability distribution of $\Delta R$ and $m_{\text{mis}}$ with $m_{\text{mis}}$ being the invariant mass of the neutrinos, denoted by $\mathcal{P}(\Delta R, m_{\text{mis}})$. These probability density functions are obtained from the MC simulation.
%
%In the Eq. \ref{eq:tautau-chi2}, the free parameters scanned are the 4-momentum components of the invisible decay products for each tau decay. In the $\tauhad$ mode, only three momentum components are scanned since a single neutrino is massless. $m_{\tau_{1,2}}^{\text{fit}}$,  $m_{H}^{\text{fit}}$ and $E_{xy,\text{miss}}^{\text{fit}}$ are the calculated tau mass, Higgs mass, and missing transverse energy with the scanned parameters. The corresponding mass resolutions, $\sigma_{\tau}$ and $\sigma_{\text{Higgs}}$, are set to 1.8~GeV and 20~GeV respectively. The $\met$ resolution is parametrized as
%\begin{equation}
%\sigma_{\text{miss}}=13.1 + 0.50\sqrt{\Sigma E_\text{T}},
%\label{eq:sigma-missing-E}
%\end{equation}
%where $\Sigma E_\text{T}$ (in GeV) is the scalar sum of transverse energy depositions of all objects and clusters. The invisible 4-momenta are obtained by minimizing the combined $\chi^2$ for each event. By adding the Higgs mass constraint term in the kinematic fit, not only is the Higgs mass resolution improved, but also the resolutions of the Higgs boson's four-momentum, and the mass of the top from which the Higgs comes.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for each search region (denoted by $\times$). 
The description of each variable is provided in the text.}}
\begin{center}
\begin{tabular}{ccccc}
\toprule\toprule 
& \multicolumn{2}{c}{$\lephad$} & \multicolumn{2}{c}{$\hadhad$} \\
Variable & 3j & $\geq$4j & 3j & $\geq$4j  \\
\midrule
$m_{\tau\tau}^{\text{fit}}$                      	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{Hq}$                                	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{T,lep}}$                              	& $\times$  & $\times$  &             & \\
$p_{\text{T,1}}$                             	& $\times$  & $\times$ & $\times$  & $\times$ \\
$p_{\text{T,2}}$                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$\met$ $\phi$ centrality                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\parallel}^{\text{miss}}$          	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\perp}^{\text{miss}}$          	& $\times$  & $\times$  &             & \\
$m_{b j_1}$                   		        & $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{lep}j}$      			        & $\times$  & $\times$  &   	  & \\
$m_{\tau j}$      			        & $\times$  & $\times$  &   	  & \\
$x_1^{\text{fit}}$				& $\times$  &	$\times$  & $\times$  & $\times$ \\
$x_2^{\text{fit}}$				& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{b j_1 j_2 }$             	   		&             & $\times$  &             & $\times$ \\ 
%\hline
\bottomrule\bottomrule
\end{tabular}
\label{tab:mva_var}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

Boosted decision trees are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
%draft 1 version
%In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
%whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\had$ contributions), 
elsewhere the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account.

A large set of potential variables were investigated in each SR separately, and only those variables that led to better discrimination
by the BDT were kept.  The BDT input variables in each SR are listed in Table~\ref{tab:mva_var} and defined in the following:

\begin{itemize}
\item $m_{\tau\tau}^{\text{fit}}$: the invariant mass of the two $\tau$-lepton candidates after the reconstruction of the neutrinos, indicating the reconstructed Higgs boson mass.
\item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\mpt$ in the $\lephad$ channel.
\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (referred to as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (referred to as particles 1 and 2 respectively) in the $\hadhad$ channel.
\item $\met$ $\phi$ centrality: a variable that quantifies the angular position of $\mpt$ relative to the visible $\tau$-lepton decay products in the transverse plane. It is defined as:
\begin{equation*}
\met\; \phi\; \mathrm{centrality} = \frac{\sin(\phi_\mathrm{miss}-\phi_1)+\sin(\phi_\mathrm{miss}-\phi_2)}{\sqrt{\sin^2(\phi_\mathrm{miss}-\phi_1)+\sin^2(\phi_\mathrm{miss}-\phi_2)}}
\end{equation*}
\noindent where $\phi_\mathrm{miss}$ denotes the azimuthal angle of $\mpt$, and $\phi_1$ and $\phi_2$ denote the azimuthal angles the two $\tau$-lepton candidates 
(the lepton and $\had$ candidate in the $\lephad$ channel, or the leading and trailing $\had$ candidates in the $\hadhad$ channel), referred to as particles 1 and 2 respectively.
%The transverse plane is transformed such that the directions of the $\tau$-lepton decay products are 
%rthogonal, and that the smaller angle between the $\tau$-lepton decay products defines the positive quadrant of the transformed plane. 
%The $\met$ $\phi$ centrality is defined as the sum of the $x$ and $y$ components of the $\mpt$ unit vector in this transformed plane.
%\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
%\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector, minus 
the magnitude of the fitted $\mpt$ vector.
\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector perpendicular to the fitted $\mpt$ vector.
\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically decaying $W$ boson.
\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
\item $m_{\tau j}$: the invariant mass of the  $\had$ candidate and the jet that has the smallest angular distance to the $\had$ candidate.
\item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
(whether $\taulep$ or $\had$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark. This variable is only defined for events with at least four jets.
\end{itemize}

Among these variables, the most discriminating are $m_{\tau\tau}^{\text{fit}}$, $p_{\text{T},2}$, $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$. A comparison between data and the predicted background for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:BDT_inputs_lephad} and~\ref{fig:BDT_inputs_hadhad}.
A good description of the data by the background model is observed in all cases.
The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:BDT}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and predicted background after preselection for the distributions of two of the most
discriminating BDT input variables in the $\lephad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
$p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added to the background prediction.
The first and the last bins in all figures contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
which is determined via a likelihood fit to data.}
\label{fig:BDT_inputs_lephad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and predicted background after preselection for the distributions of two of the most 
discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
$x_{1}^{\text{fit}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added to the background prediction.
The first and the last bins in the figures in (a) and (b) contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
which is determined via a likelihood fit to data.} 
\label{fig:BDT_inputs_hadhad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl3j/canv_.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl4j/canv_.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh3j/canv_.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.eps}} \\
\caption{$\Htautau$ search: Comparison of the distributions of the BDT discriminant after preselection of the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
and the total background (black solid) in the different search regions considered:
(a) ($\lephad$, 3j), (b) ($\lephad$, $\geq$4j), (c) ($\hadhad$, 3j), and (d) ($\hadhad$, $\geq$4j). }
\label{fig:BDT}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%-------------------------------------------------------------------------------
\section{Analysis strategy}
\label{sec:strategy_Htautau}
%-------------------------------------------------------------------------------

The analysis strategy adopted in the $\Htautau$ search follows that developed in Ref.~\cite{Chen:2015nta} but improved to apply to more signal regions.

@@

The $Wb(q)H\to q\bar{q}b(q)\tau\tau$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson and at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
In a significant fraction of the events, the lowest-$\pt$ jet from the $W$ boson decay fails the minimum $\pt$ requirement of $30~\gev$,
resulting in some decay mode signal events mixed with production mode having only three jets reconstructed.
In order to optimise the sensitivity of the search, the selected events are categorised into four SRs depending 
on the number of $\taulep$ and $\had$ candidates, and on the number of light flavored jets:
($t_h\lephad$, 2j), ($t_h\lephad$, $\geq$4j), ($t_h\hadhad$, 3j), and ($t_h\hadhad$, $\geq$4j).

This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
is missing or not (events with exactly three jets or at least four jets).
The event kinematic reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.

For the decay mode events, the selected jets are assigned to the different top-quark decay products via a criterion based on 
minimising the angular distances between light flavor jets and the visible decay product of the Higgs boson (the two tau candidates).

Finally, the four-momenta of the invisible decay products for each $\tau$-lepton decay 
are estimated from kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the the Higgs boson mass and the
measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is taken to be $20~\gev$, respectively, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_T}$, with $\sum E_T$ denoting the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson four-momentum, and hence its invariant mass, as well as the 
four-momentum of the parent top quark in the decay mode signal events, are determined with better resolution.

Following the event kinematic reconstruction, several kinematic variables that discriminate between signal and background are defined. These variables are used in the multivariate analysis discussed in the next section.

The $Wb(q)H\to l\nu b(q)\tau\tau$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown. The kinematics fit is no longer feasible. The variables calculated from the visible objects are directly used in the multivariate analysis.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
The description of each variable is provided in the text.}}
\input{\FCNCTables/Importance/xTFW/Merged}
\end{table*}

\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel. 
The description of each variable is provided in the text.}}
\input{\FCNCTables/Importance/tthML/Merged}
\end{table*}
%%%%%%%%%%%%%%%

Boosted decision trees are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
%draft 1 version
In the training, All signal events ($tuH$ and $tcH$ signal are merged with a ratio of 1:1) are used against the total SM background (including both real and fake $\had$ contributions).

A large set of potential variables were investigated in each SR separately. The discrimination of a given variable was quantified by the ``separation" and ``importance" measures provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 1\% were kept.
The BDT input variables in each SR and their importance are listed in Table~\ref{tab:mva_var} and defined in the following:
\begin{itemize}
\item $E^{T}_{miss}$ is the missing transverse momentum.
\item $p_{T,\tau}$ is the transverse momentum of the leading tau candidate.
\item $p_{T,sub-\tau}$ is the transverse momentum of the sub-leading tau candidate.
\item $p_{T,l}$ is the transverse momentum of the leading lepton.
\item $\chi^2$ is derived from kinematic fitting for the neutrinos.
\item $m_{t,SM}$ is the invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$. This variable is only defined for the 4-jet $t_hH$ and $t_ht(qH)$ events.
\item $m^{T}_{W}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as
\begin{equation}
m^{T}_{W} = \sqrt{2 p_{\text{T,lep}} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\text{lep,miss}} \right)}.  
\end{equation}
\item $m_{\tau,\tau}$ is the invariant mass of the tau candidates and reconstructed neutrinos in $t_hH$ and $t_ht(qH)$ channels. 
\item $m_{W}$ is the reconstructed invariant mass of the hadronic $W$ boson from SM top quark.
\item $m_{t,FCNC}$ is the visible invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, FCNC-jet and reconstructed neutrinos.
\item $m_{\tau\tau,vis}$ is the visible invariant mass of the di-tau candidates
\item $p_{T,\tau\tau,vis}$ is the $\pt$ of the di-tau candidates.
\item $m_{t,FCNC,vis}$ is the reconstructed visible mass of the FCNC-decaying top quark.
\item $m_{t,SM,vis}$ is the invariant mass of the lepton and the b-jet, which reflects the visible SM top mass.
\item $M(\tau\tau qjet,min)$ is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative of variable $m_{t,FCNC,vis}$.
\item $M(wjet1,wjet2,min)$ is the invariant mass of two light-flavor jet, minimized by choosing different jets, reflects the invariant mass of the W candidate, an alternative of $m_{W}$.
\item $E^{T}_{miss}$ centrality is a measure of how central the $\met$ lies between the two tau candidates in the transverse plane, and is defined as
\begin{eqnarray}
\begin{array}{l}
\met~\text{centrality} = {(x+y)}/{\sqrt{x^2+y^2}}, \\
\text{with}~x=\frac{\sin(\phi_{\text{miss}}-\phi_{\tau_1})}{\sin(\phi_{\tau_2}-\phi_{\tau_1})},  y=\frac{\sin(\phi_{\tau_2}-\phi_{\text{miss}})}{\sin(\phi_{\tau_2}-\phi_{\tau_1})} ,
\end{array}
\label{eq:eq3}
\end{eqnarray}
\item $E_{\nu,i}/E_{\tau,i},i=1,2$ is the momentum fraction carried by the visible decay products from the tau mother. It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section. For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state, which is evident in the excess around 1 in Figure \ref{fig:x12_fit}. 
\item $\Delta R(l+bjet,\tau\tau)$ is the angular distance between the lepton+b-jet and di-tau candidates.
\item $\Delta R(l,bjet)$ is the angular distance between the lepton and b-jet.
\item $\Delta R(\tau,bjet)$ is the angular distance between the tau and b-jet. If there are two taus in the event, the leading one is selected for the calculation.
\item $\eta_{\tau,max}$ is the maximum $\eta$ value among the tau candidates.
\item $\Delta R(l,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed fcnc jet.
\item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(l,\tau)$.
\item $\Delta\phi(\tau\tau,P^{T}_{miss})$ is the azimuthal angle between the $\met$ and di-tau $\pt$.
\end{itemize}
A comparison between data and the predicted background for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_lhadhad}. The comparison between the data and predicted background after preselection for the distributions of two of the most 
discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
The expected signal (dashed red) corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
The first and the last bins in the figures contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty of the background.
A good description of the data by the background model is observed in all cases.
The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{\FCNCFigures/tex/BDTinput}

\input{\FCNCFigures/tex/BDT}
